---
title: "Chrononormativity CCES 2020 Analysis"
author: "James Steur & Aleks Ksiazkiewicz"
date: "04/13/2021"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages & Data, echo=FALSE, include=FALSE, results=FALSE}
#Load in Packages & Data
library(readr)
library('devtools')
library('mirt')
#install_github('philchalmers/mirt')
library(dplyr)
packageVersion("dplyr")
library("ltm")
library('mvtnorm')
library(haven)
library(haven)
CCES20 <- read_sav("CCES20.sav")
library('stargazer')
data <- CCES20
library('ggpubr')
library(dplyr)
library(car)
library(Hmisc)
library(effectsize)
```


```{r Descriptive Statistics, echo=FALSE, include=FALSE, results=FALSE}
data$age <- (2020 - data$birthyr)
age <- (2020 - data$birthyr)
#Ages
table(age <= 24) #95. 18 to 24. 
table(age <= 34 & age > 24) #193. 25 to 34
table(age <= 44 & age > 34) #151. 35 to 44. 
table(age <= 54 & age > 44) #132. 45 to 54.
table(age <= 64 & age > 54) #218. 55 to 64.
table(age <= 74 & age > 64) #151. 65 to 74.
table(age >= 75) #60. 75 or older.
summary(age)

#Gender
data$gender

#Race
data$race #Mostly white. 731. 

#Ideology
table(data$ideo5) # Five point scale. 6 = Not sure. #1 NA. 
table(data$CC20_340a) # Seven point scale. 8 = Not sure. #1 NA.

#Party
data$pid3 # 1 = Democrat. 2 = Republican. 3 = Independent. 4 = Other. 5 = Not sure. 
data$pid7 #8 = Not sure.

#Income
data$faminc_new #97 prefer not to say. 

#Education
data$educ

#Post variables. 
#birthyr_post
#gender_post
```
```{r Ideology & Party Recode, echo=FALSE, results = FALSE}
#Ideology
ideology <- subset(data,select=c(CC20_340a))
table(ideology)
ideology <- replace(ideology, ideology == 8, NA)
table(ideology)
data$ideology <- as.numeric(unlist(ideology))
table(data$ideology)
#Party
party <- subset(data, select = c(pid7))
party[party == 8] <- NA
data$party <- party
table(party)
```


```{r Chronotype, echo=FALSE, results = FALSE}
#Address outliers.
#UIL302= Wake. UIL303 = Sleep. UIL304= Sleep Delay.
sleep <- subset(data, select = c(UIL302:UIL304))
sleep$UIL302 <- sleep$UIL302 + 20
sleep$UIL304 <- sleep$UIL304/30
sleep$GenDuration <- (sleep$UIL302 - sleep$UIL303)

sleep$GenDuration <- with(sleep, 
  ifelse(GenDuration >= 48, GenDuration - 48, 
  ifelse(GenDuration < 0, GenDuration + 48,
  GenDuration)))

sleep$GenDuration[sleep$GenDuration == 0] <- NA

sleep$UIL304 <- with(sleep,
  ifelse(GenDuration - UIL304 <= 0, NA, UIL304))

#Exclude Outliers on sleep/wake times. 
#UIL 303. Before 7PM = 1 or 2. After 6AM = 25 to 48.
sleep$UIL303 <- with(sleep,
  ifelse(UIL303 <= 2, NA, 
  ifelse(UIL303 >= 25, NA, 
  UIL303)))

#UIL 302. Before 4AM = 21 or less. After 3PM = 43 to 48.
sleep$UIL302 <- with(sleep,
  ifelse(UIL302 <= 21, NA,
  ifelse(UIL302 >= 43, NA,
  UIL302)))

#Remove sleeping fewer than 2 hours or more than 18 hours.
sleep$GenDuration <- with(sleep,
  ifelse(GenDuration <= 4, NA,
  ifelse(GenDuration >= 36, NA,
  GenDuration)))

#Midpoint of free night sleep.
sleep$GenMfs <- sleep$UIL302 - (sleep$GenDuration*0.5)

sleep$GenMfs <- (ifelse(sleep$GenMfs > 48, sleep$GenMfs - 48, sleep$GenMfs))

sleep$delay <- sleep$UIL302 - (sleep$GenDuration - sleep$UIL304)/2 
sleep$delay <- ifelse(sleep$delay > 48, sleep$delay-48, sleep$delay)

#Below 13 = Before Midnight. After 13 = After Midnight. Diving by two to get hourly unit. 
sleep$GenMfs <- (sleep$GenMfs - 13)/2
sleep$delay <- (sleep$delay - 13)/2

#Use delay for analysis.
data$chronotype_delay <- sleep$delay

#3.5 is the median amount of midpoint sleep. 
#3.5 or below = Morning. 1.
#Higher than 3.5 = Evening. 2. 

sleep$bi_type <- with(sleep,
  ifelse(delay <= 3.5, 1, 
  ifelse(delay > 3.5, 2,
         delay)))

data$bi_type <- sleep$bi_type
```


```{r Recode More Variables, echo=FALSE, results = FALSE, warning=FALSE}
#System Threat Condition 
#data$UIL301_treat #Pre-Election. 1 = Control. 2 = System Threat. 3 = System Affirming.

#Reverse Score Recoding & Summing

#Chrononomativity: UIL310-326.#8 = skipped item. 
norm_sum <- subset(data,
  select=c(UIL310:UIL326))

norm_sum[norm_sum==2] <- 0
table(data$norm_sum)


data$normativity_sum <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326 

#Conventionalism: UIL327-332.
covent_sum <- subset(data,
  select = c(UIL328, UIL329, UIL332))

#Reverse Score Items UIL327, UIL330, and UIL331
convent_sum1 <- subset(data,
  select=c(UIL327, UIL330, UIL331))
convent_sum1 <- as.data.frame((convent_sum1==1) * 5 + (convent_sum1 ==2) * 4 + (convent_sum1 ==3) * 3 + (convent_sum1 ==4) * 2 + (convent_sum1 ==5) * 1) #Reverse Score Items

data$conventionalism_sum <- convent_sum1$UIL327 + convent_sum1$UIL330 + convent_sum1$UIL331 + covent_sum$UIL328 + covent_sum$UIL329 + covent_sum$UIL332


#System Justification: UIL404-411.
system <- subset(data,
  select = c(UIL404, UIL405, UIL407, UIL408, UIL409, UIL411))
#Reverse Score Items UIL406 and UIL410.
system1 <- subset(data,
  select = c(UIL406, UIL410))
system1 <- as.data.frame((system1==1) * 5 + (system1 ==2) * 4 + (system1 ==3) * 3 + (system1 ==4) * 2 + (system1 ==5) * 1)

data$system_sum <- system1$UIL406 + system1$UIL410 + system$UIL404 + system$UIL405 + system$UIL407 + system$UIL408 + system$UIL409 + system$UIL411
```
# Pearson Correlations

Summary: The only relationships that don't have a significant relationship are Chrononormativity with Ideolodgy, Chronotype, & Conventionalism. The strongest correlations are between System Justification & Ideology (0.54), Conventionalism & Ideolodgy (0.52), and System Justification & Conventionalism (0.48).   
```{r Correlations, echo=FALSE}
#summary Chronotype
summary(data$chronotype_delay)
summary(data$normativity_sum)
summary(data$system_sum)
summary(data$conventionalism_sum)

correlations1 <- subset(data, select=c(normativity_sum, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations1)[names(correlations1) == "normativity_sum"] <- "Normativity"
names(correlations1)[names(correlations1) == "system_sum"] <- "System"
names(correlations1)[names(correlations1) == "ideology"] <- "Ideology"
names(correlations1)[names(correlations1) == "chronotype_delay"] <- "Type"
names(correlations1)[names(correlations1) == "conventionalism_sum"] <- "Conventionalism"
cor1 <- rcorr(as.matrix(correlations1))
cor1

data$normativity_sum2 <- norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations2 <- subset(data, select=c(normativity_sum2, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations2)[names(correlations2) == "normativity_sum2"] <- "Normativity"
names(correlations2)[names(correlations2) == "system_sum"] <- "System"
names(correlations2)[names(correlations2) == "ideology"] <- "Ideology"
names(correlations2)[names(correlations2) == "chronotype_delay"] <- "Type"
names(correlations2)[names(correlations2) == "conventionalism_sum"] <- "Conventionalism"
cor2 <- rcorr(as.matrix(correlations2))
cor2
```

```{r Remove Item Test Correlations, echo=FALSE, results = FALSE, warning=FALSE}
#I removed the items 
data$normativity_sum2 <- norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations2 <- subset(data, select=c(normativity_sum2, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations2)[names(correlations2) == "normativity_sum2"] <- "Normativity"
names(correlations2)[names(correlations2) == "system_sum"] <- "System"
names(correlations2)[names(correlations2) == "ideology"] <- "Ideology"
names(correlations2)[names(correlations2) == "chronotype_delay"] <- "Type"
names(correlations2)[names(correlations2) == "conventionalism_sum"] <- "Conventionalism"
cor2 <- rcorr(as.matrix(correlations2))
cor2

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324+norm_sum$UIL325+norm_sum$UIL326

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3

data$normativity_sum3 <- norm_sum$UIL310+norm_sum$UIL311+norm_sum$UIL312+norm_sum$UIL313+norm_sum$UIL314+norm_sum$UIL315+norm_sum$UIL316+norm_sum$UIL317+norm_sum$UIL318+norm_sum$UIL319+norm_sum$UIL320+norm_sum$UIL321+norm_sum$UIL322+norm_sum$UIL323+norm_sum$UIL324

correlations3 <- subset(data, select=c(normativity_sum3, system_sum, ideology, chronotype_delay, conventionalism_sum))
names(correlations3)[names(correlations3) == "normativity_sum3"] <- "Normativity"
names(correlations3)[names(correlations3) == "system_sum"] <- "System"
names(correlations3)[names(correlations3) == "ideology"] <- "Ideology"
names(correlations3)[names(correlations3) == "chronotype_delay"] <- "Type"
names(correlations3)[names(correlations3) == "conventionalism_sum"] <- "Conventionalism"
cor3 <- rcorr(as.matrix(correlations3))
cor3
```


\newpage

# Biviariate Regression Tables

System Justification relationship with Chrononormativity is significant. 
```{r, echo=FALSE}
#Create Biviariate Table Regression. Include Controls. 
correlations <- subset(data, select=c(normativity_sum, system_sum, ideology, chronotype_delay, conventionalism_sum, age, race, faminc_new, gender, educ, party))
names(correlations)[names(correlations) == "normativity_sum"] <- "Normativity"
names(correlations)[names(correlations) == "system_sum"] <- "System"
names(correlations)[names(correlations) == "ideology"] <- "Ideology"
names(correlations)[names(correlations) == "chronotype_delay"] <- "Type"
names(correlations)[names(correlations) == "conventionalism_sum"] <- "Conventionalism"
names(correlations)[names(correlations) == "faminc_new"] <- "income"
names(correlations)[names(correlations) == "educ"] <- "education"
correlations$party <- unlist(party)

mod1 <- lm(correlations$Conventionalism ~ correlations$Normativity)
mod2 <- lm(correlations$Conventionalism ~ correlations$Normativity+correlations$Ideology)
mod3 <- lm(correlations$Conventionalism ~ correlations$Normativity+correlations$Ideology+correlations$System)
mod4 <- lm(correlations$Conventionalism ~ correlations$Normativity+correlations$Ideology+correlations$System+correlations$Type)
mod17 <- lm(correlations$Conventionalism ~ correlations$Normativity+correlations$age+correlations$race+correlations$income+correlations$gender+correlations$education+correlations$party)

mod5 <- lm(correlations$Ideology ~ correlations$Normativity)
mod6 <- lm(correlations$Ideology ~ correlations$Normativity+correlations$System)
mod7 <- lm(correlations$Ideology ~ correlations$Normativity+correlations$System+correlations$Type)
mod8 <- lm(correlations$Ideology ~ correlations$Normativity+correlations$System+correlations$Type+correlations$Conventionalism)
mod18 <- lm(correlations$Ideology ~ correlations$Normativity+correlations$age+correlations$race+correlations$income+correlations$gender+correlations$education+correlations$party)

mod9 <- lm(correlations$System ~ correlations$Normativity)
mod10 <- lm(correlations$System ~ correlations$Normativity+correlations$Ideology)
mod11 <- lm(correlations$System ~ correlations$Normativity+correlations$Ideology+correlations$Conventionalism)
mod12 <- lm(correlations$System ~ correlations$Normativity+correlations$Ideology+correlations$Conventionalism+correlations$Type)
mod19 <- lm(correlations$System ~ correlations$Normativity+correlations$age+correlations$race+correlations$income+correlations$gender+correlations$education+correlations$party)

mod13 <- lm(correlations$Type ~ correlations$Normativity)
mod14 <- lm(correlations$Type ~ correlations$Normativity+correlations$Ideology)
mod15 <- lm(correlations$Type ~ correlations$Normativity+correlations$Ideology+correlations$Conventionalism)
mod16 <- lm(correlations$Type ~ correlations$Normativity+correlations$Ideology+correlations$Conventionalism+correlations$System)
mod20 <- lm(correlations$Type ~ correlations$Normativity+correlations$age+correlations$race+correlations$income+correlations$gender+correlations$education+correlations$party)

```

```{r results = 'asis', echo = FALSE}
stargazer1 <- stargazer(mod1,mod2,mod3,mod4,
     title = "Major Variables Conventionalism", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)

stargazer(mod1, mod17,
     title = "Controls Conventionalism", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)

stargazer2 <- stargazer(mod5,mod6,mod7,mod8,
     title = "Major Variables Ideology", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)

stargazer(mod5, mod18,
     title = "Controls Ideology", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)

stargazer3 <- stargazer(mod9,mod10,mod11,mod12,
     title = "Major Variables System Justification", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)

stargazer(mod9, mod19,
     title = "Controls System Justification", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)

stargazer4 <- stargazer(mod13,mod14,mod15,mod16,
     title = "Major Variables Chronotype", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)

stargazer(mod13, mod20,
     title = "Controls Chronotype", type = 'latex', single.row = TRUE, omit.stat=c("f"), header = FALSE)
```
\newpage

# IRT Models

```{r, echo=FALSE}
#IRT. Include Substantive Discussion of All This Shit. 

#2PL Binary IRT. #Norm_sum is the subset of the chrononormativity items. 
BinModel1 <- ltm(norm_sum ~ z1, IRT.param = T) #2PL model. 
#summary(BinModel1) #Difficulty, Discrimination, & EFA
#coef(BinModel1, IRTpars = T) #Coefficients
coef(BinModel1) #Nicely Formatted Difficulty & Discrimination
item.fit(BinModel1)
```
The difficulty (b) measure determines the underlying trait of Chrononormativity. The easiest way to think of these numbers are as z-scores. The set of items are roughly one standard deviation away from the mean underlying trait of Chrononormativity. 

The discrimination (a) measure determines how accurate the item is at assessing how far above and below people the difficulty parameter. Cutoffs between 1 to 4 are usually good here. Items are discriminating well. 


```{r, echo=FALSE}
#plot(BinModel1, type = "trace") ##Curves for all items at once.
#plot(BinModel1, type = "info") ##Test Curve Information
plot(BinModel1) ##Expected Score Curve
#fscores(BinModel1) ##Factor Scores

#itemfit(BinModel1, na.rm = T) ##Item Fit Stats. Removed NA's. 
#Want non-significant scores. Items with significant scores. 
# 7, 8, 16 (barely), 20, 23, 28, 30, 31, 37

#personfit(BinModel1, na.rm = T)


#Item Characteristic Curve of All Items
plot(BinModel1, type = "ICC", items = 1)
plot(BinModel1, type = "ICC", items = 2)
plot(BinModel1, type = "ICC", items = 3)
plot(BinModel1, type = "ICC", items = 4)
plot(BinModel1, type = "ICC", items = 5)
plot(BinModel1, type = "ICC", items = 6)
plot(BinModel1, type = "ICC", items = 7)
plot(BinModel1, type = "ICC", items = 8)
plot(BinModel1, type = "ICC", items = 9)
plot(BinModel1, type = "ICC", items = 10)
plot(BinModel1, type = "ICC", items = 11)
plot(BinModel1, type = "ICC", items = 12)
plot(BinModel1, type = "ICC", items = 13)
plot(BinModel1, type = "ICC", items = 14)
plot(BinModel1, type = "ICC", items = 15)
plot(BinModel1, type = "ICC", items = 16)
plot(BinModel1, type = "ICC", items = 17)
```
The Item Characteristics Curve represents the information in the table above graphically. The y-axis is the probability of a response representing the underlying trait of Chrononormativity. For example, suppose we have a 0.50 score on the y-axis that intersects with a line on the x-axis at 1. This would indicate that the item is capturing an average of one standard deviation for those who are less Chrononormative. The average score on ability is roughly one standard deviation away for all items.  

```{r, echo=FALSE}
#plot(BinModel1, type = "ICC") #All items at once
#plot(BinModel1, type = "ICC", items = 3)
plot(BinModel1, type = "IIC", items = 0) #Test Information Function
```

The Test Information Function graph takes all the items and determines the probability along each point for the underlying trait of Chrononormativity. This curve tells us where the most "information" is present. We are getting the most information at roughly one standard deviation away from the mean. We're getting a lot of information about people who tend to score lower on Chrononormativity measures (do whatever you want whenever you want), so this set of items may not tell us the most about people who score higher on Chrononormativity measures (there are strict times of day you should do things.)

```{r, echo=FALSE}
#Factor_Scores <- factor.scores(BinModel1) 
#print(Factor_Scores)
#See Frequency of How Often People Select

#person.fit(BinModel1)
#item.fit(BinModel1)
```



# Treatments & Control: Chrononormativity Mean Differences

Summary of this section: it looks like there isn't a statistically significant relationship based on the box-plot and table showing the means of the observations. It looks like one possible explanation is that a high number of participants are fine with people doing a lot of stuff whenever they want based on the histogram. 

```{r Differeince in Means, echo=FALSE, include=FALSE, results=FALSE}
#Two Way ANOVA
anova <- subset(data, select=c(normativity_sum, UIL301_treat, bi_type))
anova$Chrononormativity <- anova$normativity_sum
anova$Chronotype <- anova$bi_type
anova$Treatment <- anova$UIL301_treat

anova$Treatment <- factor(anova$Treatment, 
                  levels = c(1, 2, 3),
                  labels = c("Control", "Threat", "Affirming"))

anova$Chronotype <- factor(anova$Chronotype, 
                  levels = c(1, 2),
                  labels = c("Morning", "Evening"))
```

```{r, warning = FALSE, echo=FALSE}
group_by(anova, Treatment, Chronotype) %>%
  summarise(
    count = n(),
    mean = mean(Chrononormativity, na.rm = TRUE),
    sd = sd(Chrononormativity, na.rm = TRUE)
  )

```


```{r, echo=FALSE, warning = FALSE}
ggboxplot(anova, x = "Treatment", y = "Chrononormativity", color = "Chronotype",
          palette = c("#00AFBB", "#E7B800"))

two.way <- aov(Chrononormativity ~ Treatment*Chronotype, data = anova)
summary(two.way)


hist(data$normativity_sum,
     main = "Chrononormativity Responses",
     xlim = c(0,15),
     ylim = c(0,700),
     xlab = "Chrononormativity", 
     col = "blue")

my_anova <- aov(Chrononormativity ~ Treatment*Chronotype, data = anova)
#imbalance <- Anova(my_anova, type = "III")

summary(my_anova)
Anova(two.way, type = "III")
```


```{r, echo=FALSE, warning = FALSE}
#Two Way ANOVA: Other Variables
anova1 <- subset(data, select=c(normativity_sum, UIL301_treat, bi_type, conventionalism_sum, system_sum))
anova1$Chrononormativity <- anova$normativity_sum
anova1$Chronotype <- anova$bi_type
anova1$Treatment <- anova$UIL301_treat
anova1$Conventionalism <- anova1$conventionalism_sum
anova1$System <- anova1$system_sum

anova1$Treatment <- factor(anova1$Treatment, 
                  levels = c(1, 2, 3),
                  labels = c("Control", "Threat", "Affirming"))

anova1$Chronotype <- factor(anova1$Chronotype, 
                  levels = c(1, 2),
                  labels = c("Morning", "Evening"))

group_by(anova1, Treatment, Chronotype) %>%
  summarise(
    count = n(),
    mean = mean(Conventionalism, na.rm = TRUE),
    sd = sd(Conventionalism, na.rm = TRUE)
  )

group_by(anova1, Treatment, Chronotype) %>%
  summarise(
    count = n(),
    mean = mean(System, na.rm = TRUE),
    sd = sd(System, na.rm = TRUE)
  )

ggboxplot(anova1, x = "Treatment", y = "Conventionalism", color = "Chronotype",
          palette = c("#00AFBB", "#E7B800"))

hist(data$conventionalism_sum,
     main = "Conventionalism Responses",
     xlim = c(5,30),
     ylim = c(0,250),
     xlab = "Conventionalism", 
     col = "blue")

ggboxplot(anova1, x = "Treatment", y = "System", color = "Chronotype",
          palette = c("#00AFBB", "#E7B800"))

two.way <- aov(System ~ Treatment*Chronotype, data = anova1)
summary(two.way)


hist(data$system_sum,
     main = "System Responses",
     xlim = c(0,45),
     ylim = c(0,125),
     xlab = "System", 
     col = "blue")

#my_anova <- aov(Conventionalism ~ Treatment*Chronotype, data = anova)
```
```{r}
two.way <- aov(Conventionalism ~ Treatment*Chronotype, data = anova1)
summary(two.way)
Anova(two.way, type = "III")

two.way <- aov(Conventionalism ~ Treatment*Chronotype, data = anova1)
summary(two.way)
Anova(two.way, type = "III")
```

```{r}
Threat <- as.numeric(unlist(subset(anova, Treatment=="Threat", 
       select = normativity_sum)))
Affirming <- as.numeric(unlist(subset(anova, Treatment=="Affirming", 
       select = normativity_sum)))
Control <- as.numeric(unlist(subset(anova, Treatment=="Control", 
       select = normativity_sum)))
class(Threat)
#Effect Sizes
cohens_d(Control, Threat)
hedges_g(Control, Threat)
glass_delta(Control, Threat)

cohens_d(Control, Affirming)
hedges_g(Control, Affirming)
glass_delta(Control, Affirming)


my_anova10 <- aov(Chrononormativity ~ Treatment*Chronotype, data = anova)
eta_squared(my_anova10)
omega_squared(my_anova10)
epsilon_squared(my_anova10)
cohens_f(my_anova10)
cohens_f_squared(my_anova10)
```

